---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# freshdeskr: An R Package for the Freshdesk API

**Authors:** [John Januszczak](https://github.com/jjanuszczak)<br/>
**License:** [MIT](https://opensource.org/licenses/MIT)

[![Travis-CI Build Status](https://travis-ci.org/jjanuszczak/freshdeskr.svg?branch=master)](https://travis-ci.org/jjanuszczak/freshdeskr)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This R package acts as a wrapper for the [Freshdesk API](https://developers.freshdesk.com/api/). Currently, the package contains functionality for retrieving ticket, agent, company and contact data from Freshdesk. This data can be used in subsequent analysis.

## Installation

You can install freshdeskr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jjanuszczak/freshdeskr")
```

## Examples

The following examples demonstrate how to retrieve ticket, agent, company and contact data from Freshdesk.

### Tickets

Using the `tickets` method, retrieve a data frame of tickets and get the status, priority and subject of all tickets updated since May 1, 2018:

```{r credentials, echo=FALSE}
my_domain <- Sys.getenv("FRESHDESK_DOMAIN")
my_api_key <- Sys.getenv("FRESHDESK_API_KEY")
```

```{r example0, warning=FALSE}
library(freshdeskr)

# create a client
fc <- freshdesk_client(my_domain, my_api_key)

# gets tickets undated since May 1, 2018
ticket_data <- tickets(fc, updated_since = "2018-05-01")

# subset by columns of interest
ticket_data[, c("subject", "status", "priority")]
```

### Companies

Using the `companies` method, get a list of companies:

```{r example00}
# retrieve all companies
comps <- companies(fc, max_records = 2)

head(comps)
```

### Agents

Using the `agent` method, get data on an agent based on the agent ID:

```{r example0a}
# get agent based on agent id
ag <- agent(fc, 42001318960)

# get the agent's name and email
cat(ag$contact$name, ",", ag$contact$email)
```

### Contacts

Use the `contacts` method to add contact name and email to a list of tickets

```{r example0b}
# get tickets updated since January 1, 2018
ticket_date <- tickets(fc, updated_since = "2018-01-01")

# get data on all contacts
contact_data <- contacts(fc)

# join data frames
tickets_with_contact_info <- merge(x = ticket_data, y = contact_data, by.x = "requester_id", by.y = "id")

# show contact name and email with ticket number and subject
tickets_with_contact_info[, c("id", "subject", "name", "email")]
```

## Interacting Directly with the API

For lower level control and flexibility, use the `freshdesk_api` function to call the Freshdesk API directly to retrieve the following:

* parsed json from the respose object
* the httr response object
* rate limit status

In the following example, we retrieve the ticket subject from the parsed response object:

```{r example1}
library(freshdeskr)

# create a client
fc <- freshdesk_client(my_domain, my_api_key)

# query the api and view the details of ticket #3
apidata <- freshdesk_api(fc, "/api/v2/tickets/3")

# get useful data from the parsed response
apidata$content$subject
```

One can also inspect the http response directly, for example:

```{r example2}
apidata$response$status_code
```

Rate limit information is also returned by calls to the `freshdesk_api` function:

```{r example3}
# get current status of rate limit at time of api call
apidata$rate_limit_remaining
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
