---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# freshdeskr: An R Package for the Freshdesk API

**Authors:** [John Januszczak](https://github.com/jjanuszczak)<br/>
**License:** [MIT](https://opensource.org/licenses/MIT)

[![Travis-CI Build Status](https://travis-ci.org/jjanuszczak/freshdeskr.svg?branch=master)](https://travis-ci.org/jjanuszczak/freshdeskr)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This R package acts as a wrapper for the [Freshdesk API](https://developers.freshdesk.com/api/). This is a work in progress. Check back for updates.

## Installation

You can install freshdeskr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jjanuszczak/freshdeskr")
```

## Example

Using the `tickets` method, retrieve a data frame of tickets and get the status, priority and subject of all tickets updated in May 2018:

```{r credentials, echo=FALSE}
my_domain <- Sys.getenv("FRESHDESK_DOMAIN")
my_api_key <- Sys.getenv("FRESHDESK_API_KEY")
```

```{r example0, warning=FALSE}
library(freshdeskr)

# create a client
fc <- freshdesk_client(my_domain, my_api_key)

# gets tickets 
ticket_data <- tickets(fc)

# filter by date
# dates in the dataframe are of type POSIXlt so they can be easily filtered by date or time part 
# (e..g month, year, etc.) remembering that months index from 0-11 and year is years since 1900
ticket_data <- ticket_data[ticket_data$updated_at$mon + 1 == 5 & ticket_data$updated_at$year + 1900 == 2018, ]

# subset by columns of interest
ticket_data[, c("subject", "status", "priority")]
```

Using the `freshdesk_api` function you can call the Freshdesk API directly to retrieve the following:

* parsed json from the respose object
* the httr response object
* rate limit status

```{r example1}
library(freshdeskr)

# create a client
fc <- freshdesk_client(my_domain, my_api_key)

# query the api and view the details of ticket #3
apidata <- freshdesk_api(fc, "/api/v2/tickets/3")

# get useful data from the parsed response
apidata$content$subject
```

```{r example2}
# get current status of rate limit at time of api call
apidata$rate_limit_remaining
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
